High Contrast Coronagraphy

### 2025-01-08 src/tex/ms.tex
accepted

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{@mkenworthy}

% Abstract with filler text
\begin{abstract}
caeast
    Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
    Donec vehicula augue eu neque, morbi tristique senectus et netus et.
    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
    Phasellus eu tellus sit amet tortor gravida placerat.
    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
    Praesent eget sem vel leo ultrices bibendum.
    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
    Curabitur auctor semper nulla donec varius orci eget risus.
    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
    Duis eget orci sit amet orci dignissim rutrum.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
Donec vehicula augue eu neque, morbi tristique senectus et netus et.
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
Phasellus eu tellus sit amet tortor gravida placerat.
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
Praesent eget sem vel leo ultrices bibendum.
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
Curabitur auctor semper nulla donec varius orci eget risus.
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi.
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae.
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna.
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante.
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient.
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis.
Pellentesque cursus luctus mauris \citep{Luger2021}.

\bibliography{bib}

>>>>

\documentclass[letterpaper]{ar-1col}
\usepackage{showyourwork}
\usepackage[letterpaper]{geometry}

\usepackage{natbib}
\usepackage{amsmath}
\usepackage{color}

\usepackage{hyperref}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}% http://ctan.org/pkg/booktabs
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\hypersetup{colorlinks=true,allcolors=[rgb]{0,0,0.8}}

\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\mum}{$\mu$m}
\newcommand{\ld}{$\lambda/D$}
\newcommand{\fourier}[1]{\mathcal{F}\{#1\}}
\newcommand{\invfourier}[1]{\mathcal{F}^{-1}\{#1\}}
\newcommand{\acc}[1]{\entry{\acs{#1}}{\acl{#1}}}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{multicol}%for multiple columns
\usepackage{etoolbox}

\usepackage{graphbox}

\setcounter{secnumdepth}{4}
\usepackage{url}

% https://tex.stackexchange.com/questions/163451/total-number-of-citations
\usepackage{totcount}
\usepackage[nolist,nohyperlinks]{acronym}

\begin{acronym}
    \acro{aplc}[APLC]   {Apodized Phase Lyot Coronagraph}
    \acro{paplc}[PAPLC] {Phase Apodized Phase Lyot Coronagraph}
    \acro  {psf}[PSF]   {Point Spread Function}
    \acro  {iwa}[IWA]   {Inner Working Angle}
    \acro  {owa}[OWA]   {Outer Working Angle}
    \acro  {ao}[AO]     {Adaptive Optics}
    \acro  {fpm}[FPM]   {Focal Plane Mask}
    \acro  {ppm}[PPM]   {Pupil Plane Mask}
    \acro  {hz}[HZ]     {Habitable Zone}
    \acro  {hlc}[HLC]   {Hybrid Lyot Coronagraph}
    \acro {fpwfs}[FPWFS]{Focal Plane Wavefront Sensing}
    \acro  {fwhm}[FWHM] {Full Width Half Maximum}
    \acro  {fqpm}[FQPM] {Four Quadrant Phase Mask}
    \acro  {agpm}[AGPM] {Annular Groove Phase Mask}
    \acro  {ovc}[OVC]   {Optical Vortex Coronagraph}
    \acro  {pp}[PP]     {Pupil Plane}
    \acro  {fp}[FP]     {Focal Plane}
    \acro  {sam}[SAM]     {Sparse Aperture Masking}
    \acro  {scar}[SCAR]     {Single-mode Complex Amplitude Refinement}
    \acro  {hci}[HCI]   {High Contrast Imaging}
    \acro  {dm}[DM]     {Deformable Mirror}
    \acro  {wfs}[WFS]   {Wavefront Sensor}
    \acro  {zwfs}[ZWFS] {Zernike Wavefront Sensor}
    \acro  {sphere}[SPHERE]{Spectro-Polarimetric High-contrast Exoplanet REsearch}
    \acro  {scfp}[SCFP] {Science Camera Focal Plane}
    \acro  {smd}[SMD]   {Spatial Mode Demultiplexing}
    \acro  {ncpa}[NCPA] {Non-Common Path Aberration}
    \acro  {mspl}[MSPL] {Mode-selective Photonic Lantern}
    \acro  {elt}[ELT]   {Extremely Large Telescope}
    \acro  {jwst}[JWST] {James Webb Space Telescope}
    \acro  {gmt}[GMT]   {Giant Magellan Telescope}
    \acro  {tmt}[TMT]   {Thirty Metre Telescope}
    \acro  {spp}[SPP]     {Shaped Pupil Plate}
    \acro  {efc}[EFC]     {Electric Field Conjugation}
    \acro  {scc}[SCC]   {Self Coherent Camera}
    \acro  {piaa}[PIAA] {Phase Induced Amplitude Apodization}
    \acro  {piaacmc}[PIAACMC] {Phase Induced Amplitude Apodization Complex Mask Coronagraph}
    \acro  {fast}[FAST] {Fast Atmospheric SCC}
    \acro  {smscc}[SM-SCC] {Spectrally Modulated SCC}
    \acro  {app}[APP]   {Apodizing Phase Plate}
    \acro  {gvapp}[gvAPP]   {grating vector Apodizing Phase Plate}
    \acro  {vvc}[VVC]   {Vector Vortex Coronagraph}
   \acro  {vfn}[VFN]    {Vortex Fibre Nulling}
   \acro  {ravc}[RAVC]  {Ring Apodized Vortex Coronagraph}
    \acro  {hwo}[HWO]   {Habitable Worlds Observatory}
    \acro  {hci}[HCI]   {High Contrast Imaging}
%% Define a custom plural form of an acronym   
    \acrodefplural{psf}[PSFs]   {Point Spread Functions}
    \acrodefplural{dm}[DMs]     {Deformable Mirrors}
    \acrodefplural{wfs}[WFSs]   {Wavefront Sensors}
    \acrodefplural{elt}[ELTs]   {Extremely Large Telescopes}
    \acrodefplural{ncpa}[NCPAs] {Non-Common Path Aberrations}
%% Preferably, put all acronym definitions in one file and load it
%   \input{acros.tex}
\end{acronym}

\newtotcounter{citnum} %From the package documentation
\def\oldbibitem{} \let\oldbibitem=\bibitem
\def\bibitem{\stepcounter{citnum}\oldbibitem}

% Metadata Information
\jname{Annu. Rev. Astron. Astrophys.}
\jvol{AA}
\jyear{2025}
\doi{10.1146/TBD}

% autoref formatting
\def\sectionautorefname{Section}
\let\subsectionautorefname\sectionautorefname
\let\subsubsectionautorefname\sectionautorefname

% macros
\newcommand{\apjl}{Astrophysical Journal Letters}
\newcommand{\aj}{Astronomical Journal}
\newcommand{\ao}{Applied Optics}
\newcommand{\procspie}{SPIE Proceedings}
\newcommand{\apj}{Astrophysical Journal}
\newcommand{\apjs}{Astrophysical Journal Supplement}
\newcommand{\pasp}{Publications of the Astronomical Society of the Pacific}
\newcommand{\jgr}{Journal of Geophysical Research}
\newcommand{\aap}{Astronomy and Astrophysics}
\newcommand{\aapr}{Astronomy and Astrophysics Review}
\newcommand{\mnras}{Monthly Notices of the Royal Astronomical Society}
\newcommand{\actaa}{Acta Astronomica}
\newcommand{\nat}{Nature}
\newcommand{\prl}{Physical Review Letters}
\newcommand{\prd}{Physical Review D}
\newcommand{\ssr}{Space Science Reviews}
\newcommand{\araa}{Annual Review of Astronomy and Astrophysics}
\newcommand{\jrasc}{Journal of the Royal Astronomical Society of Canada}
% Symbols
\newcommand{\ydata}{\ensuremath{\boldsymbol{y}}}
\newcommand{\hyperparams}{\ensuremath{\boldsymbol{\phi}}}
\newcommand{\meanparams}{\ensuremath{\boldsymbol{\theta}}}
\newcommand{\dt}{\ensuremath{\tau}}
\newcommand{\amplitude}{\ensuremath{\alpha}}
\newcommand{\lengthscale}{\ensuremath{\lambda}}

\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\project}[1]{\textsf{#1}}

% Document starts
\begin{document}

% Page header
\markboth{Kenworthy \& Haffert}{HCC}

%TC:ignore

% Title
\title{High Contrast Coronagraphy}

%Authors, affiliations address.
\author{Matthew Kenworthy$^1$ and Sebastiaan Haffert$^{1,2}$
  \affil{$^1$Leiden Observatory, Niels Bohrweg 2, Leiden 2300RA, The Netherlands; email: kenworthy@strw.leidenuniv.nl}
  \affil{$^2$University of Arizona, Steward Observatory, 933 N. Cherry Avenue, Tucson, Arizona, United States; email: haffert@strw.leidenuniv.nl}}

% Abstracts should include 3–5 bullet points citing actual conclusions of the review. Please limit the abstract to no more than 200 words, including the bullet points. If using TeX, use a “\hangindent=.3cm$bullet$” command at the beginning of each bullet-point paragraph. [The “\begin{itemize}” environment may require the use of a “hardwired” line return (i.e., the ”\\” command) within the environment, as lines may not automatically return in the compiled version.]
%Abstract
\begin{abstract}
Imaging terrestrial exoplanets around nearby stars is a formidable technical challenge, requiring the development of coronagraphs to suppress the stellar halo of diffracted light at the location of the planet.
%
In this Review, we derive the science requirement for high contrast imaging, give an overview of diffraction theory and the Lyot coronagraph, and define the parameters used in our optimization.
%
We detail the working principles of coronagraphs both in laboratory and on-sky with current high contrast instruments, and detail the required algorithms and processes necessary for terrestrial planet imaging with the extremely large telescopes and proposed space telescope missions.

\begin{itemize}
    \item Imaging terrestrial planets around nearby stars is possible with \\ 
    a combination of coronagraphs and active wavefront control \\
    using feedback from wavefront sensors.
    \item Ground based 8-40m class telescopes can target the habitable \\ 
    zone around nearby M dwarf stars with contrasts of $10^{-7}$ and \\
    space telescopes can search around solar-type stars with \\
    contrasts of $10^{-10}$.
    \item Focal plane wavefront sensing, hybrid coronagraph designs and \\
    multiple closed loops providing active correction are required \\
    to reach the highest sensitivities.
    \item Polarization effects need to be mitigated for reaching $10^{-10}$ \\ contrasts whilst keeping exoplanet yields as high as possible.
    \item Recent technology development, including photonics and MKIDs, \\
    will be folded into high contrast instruments.
\end{itemize}

\end{abstract}

%Keywords, etc.
\begin{keywords}
 Optics, coronagraphs, exoplanets, high contrast, computational methods
\end{keywords}
\maketitle

%Table of Contents
\tableofcontents

\section{INTRODUCTION}
\label{sec:intro}

% High contrast imaging, Lyot corongraph, 2000's development

%TC:endignore

Initially developed to image the Sun's corona without the need for a Solar eclipse \citep{Lyot33}, one of the most significant science drivers for the latest coronagraphs is in the detection and characterisation of circumstellar material and planets around nearby stars.
%
Young self-luminous gas giant exoplanets have been discovered around young stars \citep[see ][ for a review of these detections]{Zurlo24} both in the nearby Galactic field and further away in young stellar OB associations (out to 400 pc), typically these exoplanets have luminosities of $10^{-4}-10^{-6}$ of their parent star at angular separations up to a few arcseconds.

The search for life beyond the Earth has focused on the idea that water is an essential part of life cycles elsewhere in the Universe, as it is a polar solvent formed from two elements that are found in abundance throughout the Galaxy.
%
Places where water can exist in its liquid state form prime locations for these searches, notably Earth-like planets and ice moons that have a liquid water ocean underneath an ice layer.
%
The region around a star where liquid water can exist on the surface of a terrestrial planet (with appropriate atmospheric pressure) is referred to as the \ac{hz}; for the Sun this is from 0.9-1.2 au but this can move as the luminosity of stars change with time.

At optical wavelengths, exoplanets are not self-luminous but instead reflect the light of their parent star.
%
For an Earth analogue with similar radius, albedo and effective temperature orbiting around a solar-type star 10 parsecs away, the typical amount of reflected light in the optical is $10^{-10}$ of the central star at a separation of 0.1 arcseconds at maximum elongation.
%
The technical challenge is in distinguishing the light of the parent star from the light of the planet.
%
Planetary systems that are closer to the Sun have two benefits: one that is twice as close as the other will have double the angular separation between the star and planet, and from the inverse square law, four times more flux is received from the planet.
%
For direct imaging, therefore, the closest stars to the Sun are the ones that are studied for the presence of directly imaged exoplanets.
%
On average there are more M dwarf stars close to the Sun than other solar type stars: in a volume limited (20 parsec) sample around the Sun, there are $\sim 140$ solar G-type stars, and on the order of 1900 M-dwarf stars \citep{Kirkpatrick24}.
%
For solar type stars, the contrast required in the optical wavelengths is on the order of $10^{-10}$ for terrestrial planets in the \ac{hz}, but for smaller mass stars with lower luminosities, the contrast is $10^{-7}$ for M dwarfs - for stars around the Sun this is shown in Figure~\ref{fig:nstars}.

\begin{figure}[ht]
  \centering
  \script{plot_flux_ratio.py}
  \includegraphics[width=1.0\linewidth]{figures/flux_ratio.pdf}
  \caption{Angular separation versus contrast for directly imaged exoplanets.
  %
  The upper right part of the figure shows known self-luminous gas giant planets \citep{Lacy20}.
  %
  The lines show  $5\sigma$ point source contrast limits from recent instruments and surveys.
  %
  Figure plot and data from \citet{Bailey24}.
  %
  Grey triangles are the expected contrasts for reflected light from known radial velocity detected exoplanets \citep{Bataltha18}.
  %
  Circles represent reflected light estimates for 1 Earth radius planets, assuming one planet per star within 20 parsecs of the Sun in the Habitable Zone at maximum elongation.
  %
  Grey points are planets that are fainter than 30th magnitude in $V$.
  %
  The color represents the effective temperature of the star.
  %
  The larger the point, the closer the stellar system is to the Sun.
  %
  Reflected light data from \href{https://subarutelescope.org/staff/guyon/04research.web/14hzplanetsELTs.web/catalog.web/content.html}{Guyon (2024) web page}.  
  %{\em ELT goal:} Possible range of near-IR post-processed detection limits for next generation extremely large telescopes. 
% -- HabEx: Goal 5-sigma post-processed contrast.  IWA $\sim$ 2.5 \ld{} @ 450nm; OWA $\sim$ 32 \ld{} at 1micron (source: B. Mennesson, personal communication)
% -- JWST NIRCAM: 5-sigma post-processed [ADI+RDI] contrast curve for F356W-band from program ERS 1386 on HIP 65426. Data inside the nominal IWA of 0.64'' are not displayed (source: Carter+2022)
% -- HST NICMOS: 5-sigma post-processed [KLIP + match filter] contrast curve for F160W-band; this was the BEST contrast curve from the ALICE program (HST program 7226, and others), with typical integration times of 2hr (600-1600s range). (source: E. Choquet, personal communication) Please cite \url{http://adsabs.harvard.edu/abs/2014SPIE.9143E..57C}.
% -- HST STIS: Bar5 coronagraph 5-sigma post-processed [KLIP] contrast curve; 162sec exposure. Photon noise is a significant contributor beyond 0.7''. (source: STIS handbook) This program observed HD 38393 at 9 roll angles with 9 dithers per roll angle. No filter was used, so the bandpass is ~200-1030nm. Total exposure time = 810*.2sec = 2.7 minutes, and is therefore moderately photon limited at large angles. Assuming photon noise adds in quadrature with speckle residuals to produce the KLIP contrast, the photon noise is $>$50\% the amplitude of the speckle noise beyond $\sim$0.7''.
% -- HST ACS: 5-sigma post-processed [simple image difference] contrast curve of 2x100sec Arcturus observation in F606W with 1.8'' occulter. The two exposures were taken 85 minutes apart, to simulate a typical 2-roll (2 orbit) ADI observation. The contrast curve is a simple difference of the images, after registration. (source: J. Krist, personal communication)
% -- SPHERE: 5 sigma post-processed [SDI] contrast curve for an ~1hr integration on Sirius. At separations $<0.7''$ the curve is for IFS YJH, while $>0.7''$ is IRDIS K12; $0.7''$ is the crossover point where IRDIS becomes better than IFS. Integration times: IRDIS = 88 min, IFS = 59min; difference is due to detector overheads. FOV rotation = 106dgr. The SDI reduction assumes the planet-star contrast is constant at all wavelengths. (Source: Vigan et al. 2015 MNRAS 454 129)
% -- GPI: 5-sigma post-processed [KLIP + forward model match filter] contrast curve for H-band IFS mode, 1hr integration. Calculated from an 11min H-band IFS observation of Sirius, reduced with Jean-Baptiste Ruffio's Forward Model Matched Filter code, optimized for L-type objects. The 60min column is $\sqrt(t)$ scaling from the 11min column, for a more equal comparison to the SPHERE 59min IFS contrast curve. (source: B. Macintosh, personal communication).
% -- Roman CGI narrow FOV imaging prediction: Modeled 5-sigma post-processed [RDI\&fpp=2] contrast curve for Band 1 imaging of a V=5 G0V star with the HLC coronagraph. The model observation uses an optimistic estimate for instrument and observatory performance and for 21mo into mission. Integration time is 100hr. Updates include: flight mask, performance tables, bench warping and DM temperature stability, coating reflectivity. Source: \url{https://github.com/hsergi/Roman_Coronagraph_ETC/tree/main/tables/}, 12/02/2021 version.
% -- Roman CGI Single Slit, Prism-based Spectroscopy prediction: Modeled 5-sigma post-processed [RDI\&fpp=1.22] contrast curve for Band 3 spectroscopy of a V=5 G0V star with the SPC bowtie coronagraph. The model observation uses an optimistic estimate for instrument and observatory and for 21mo into mission. Integration time is  400hr. Updates include: flight mask, performance tables, bench warping and DM temperature stability, coating reflectivity. Source: \url{https://github.com/hsergi/Roman_Coronagraph_ETC/tree/main/tables/}, 12/02/2021 version.
% -- Roman CGI wide FOV imaging prediction: Modeled 5-sigma post-processed [RDI\&fpp=2] contrast curve for Band 4 imaging of a V=5 G0V star with the HLC coronagraph. The model observation uses an optimistic estimate for instrument and observatory performance and for 21mo into mission. Integration time is 100hr. Updates include: flight mask, performance tables, bench warping and DM temperature stability, coating reflectivity. Source: \url{https://github.com/hsergi/Roman_Coronagraph_ETC/tree/main/tables/}, 12/02/2021 version.
% -- DI: Selected known self-luminous Directly Imaged (DI) exoplanets with known H-band contrasts. Predicted fluxes at Bands  1 and 3 are either from B. Lacy or from either COND $(T_{eff}\le 1200K)$ or BT-SETTL models. For COND/BT values, WFC3 filters that approximate Roman's coronagraph instrument bands were used (547nm 10\% and 763nm 10\%), because WFC3 colors are already provided with the model grids.
% -- Earth (==1E-10) \& Jupiter (albedo=0.52) at quadrature as seen from 10 pc. (Jupiter albedo: Traub \& Oppenheimer, Direct Imaging chapter of Seager Exoplanets textbook, Table 3)
% -- RV: Predicted reflected light flux ratios at quadrature for known RV planets, from the Imaging Mission Database. We assume clouds with $f_{sed} = 3$. Dark gray triangles signify V $<$ 5 host stars; light grey triangles signify  $5 < V < 6$ host stars. Commented lines are planets that would meet criteria, but whose host stars are known binaries and/or too large in angular diameter. See \url{https://plandb.sioslab.com/about.php} for Imaging Mission Database acknowledgements policy.
}
  \label{fig:nstars}
\end{figure}

The markers for biosignatures also set the parameters (such as wavelength and bandwidth) that form part of the design decision.
%
Spectra of Earthshine (light reflected from the Earth by the non-Sun lit portion of the Moon) from 0.5 to 2.4 microns show \ce{O2}, \ce{O3}, \ce{CO2}, \ce{CH4} and \ce{H2O} \citep{Turnbull06}, and there are many discussions about the possible biomarker molecules that should be searched for and characterised as evidence for biosignatures \citep[see the reviews of ][]{2016AsBio..16..465S,2017ARAA..55..433K,2018AsBio..18..663S}.
%
It is clear that the unambiguous detection of life will require not one singular detection of a molecule, but will be the combination of several different lines of evidence.
%
We focus on the technical challenges for imaging a rocky terrestrial planet around a nearby star in our Galaxy.

\section{From Maxwell's Equations to Wavefronts}\label{sec:maxwell}

\begin{table}
\caption{Definition of physical quantities}\label{tab1}
\begin{center}
\begin{tabular}{@{}l|l|l|l@{}}
\hline
$i$ & The imaginary unit & $c$ & Speed of light in a vacuum \\\hline
$\vec{E}$ & Electric field & $\vec{H}$ & Magnetic field \\\hline
$\mathcal{D}$ & Displacement field & $\mathcal{B}$ & Magnetizing field \\\hline
$\epsilon$ & Electric permittivity & $\epsilon_0$ & Electric permittivity of vacuum \\\hline
$\mu$ & Magnetic permittivity & $\mu_0$ & Magnetic permittivity of vacuum \\\hline
$\omega$ & Wavenumber & $\vec{k}$ & Wavevector \\\hline
$\lambda$ & Wavelength & $\lambda_0$ & Center wavelength in the bandpass \\\hline
$\Pi$ & The telescope pupil function & $\Delta\lambda$ & The width of the bandpass \\\hline
$D$ & Diameter of the pupil & $n$ & (Complex) refractive index of macroscopic media \\\hline
$\mathcal{F}_{x,y}[\cdot]$ & Fourier transform operator & $\mathcal{F}^{-1}_{x,y}[\cdot]$ & Inverse Fourier transform operator \\\hline
$C_\lambda[\cdot]$ & A general coronagraph propagation operator & $\Psi_\lambda[\vec{k}]$ & Coronagraphic image \\\hline
$\phi$ & The phase of the electric field & $\alpha$ & The amplitude of the electric field \\\hline
\hline
\end{tabular}
\end{center}
\end{table}

The vast majority of energy from astrophysical objects arrives at our telescopes in the form of electromagnetic radiation.
%
This time-dependent interaction is described by Maxwell's equations (with relevant physical quantities defined in Table \ref{tab1}),

\begin{equation}
\begin{aligned}
\frac{\partial\mathcal{D}}{\partial t} \quad & = \quad \nabla\times\mathcal{H},   & \quad \text{(Faraday's law)} \\[5pt]
\frac{\partial\mathcal{B}}{\partial t} \quad & = \quad -\nabla\times\mathcal{E},  & \quad \text{(Ampere's Law)}   \\[5pt]
\nabla\cdot\mathcal{B}                 \quad & = \quad 0,                         & \quad \text{(Gauss's law)}   \\[5pt]
\nabla\cdot\mathcal{D}                 \quad & = \quad 0.                         & \quad \text{(Coulomb's law)}
\end{aligned}
\end{equation}

This form of Maxwell's equations is in the material form without any charge and current sources.
%
The material form is used to describe the propagation of electromagnetic fields inside matter.
%
This set of equations is completed by describing the particular matter of the medium with the constitutive relations, $\mathcal{D}=\epsilon \mathcal{E}$ and $\mathcal{B}=\mu \mathcal{H}$. 
%
Here $\epsilon$ and $\mu$ are the permittivity and magnetic permeability, respectively.
%
The wave equation for electromagnetic waves can be derived by taking the curl of Ampere's law.
%
This gives us the classic wave equation if we assume that the EM wave propagates in isotropic and homogeneous materials,
\begin{equation}
\label{eq:wave_eq}
\begin{aligned}
\mu \epsilon \frac{\partial^2 \mathcal{E}}{\partial t^2} - \nabla^2\mathcal{E} = 0 .
\end{aligned}
\end{equation}
We consider a purely monochromatic EM wave with frequency $\omega$.
%
The wave function is then $\mathcal{E}=\psi(r) e^{iwt}$ with $\psi(r)$ describing the spatial distribution.
%
Substituting this relation into Equation \ref{eq:wave_eq},
\begin{equation}
\nabla^2\mathcal{E} +\mu \epsilon \omega^2 \mathcal{E} = 0.
\end{equation}
The usual definition of the permittivity and permeability are $\epsilon=\epsilon_r \epsilon_0$ and $\mu=\mu_r \mu_0$ with $\epsilon_r$ and $\mu_r$ the relative permittivity and permeability compared to that of vacuum, $\epsilon_0$ and $\mu_0$.
%
In optics most glasses and materials are defined by their refractive index $n$ which is related to permittivity as $\epsilon_r = n^2$ and many of these are also non-magnetic which means that $\mu_r=1$.
%
Substituting this will give us the classic Helmholtz equation
\begin{equation}
\nabla^2\mathcal{E} + n^2k^2 \mathcal{E} = 0,
\end{equation}
We made use of the fact that the speed of light is $c = \frac{1}{\sqrt{\epsilon_0\mu_0}}$ and that $k = c\omega$ is the wave number.
%
The propagation through an optical system has a preferential direction that is usually defined along the z-axis.
%
The z-axis evolution can be derived by separating the spatial components into the z component and the perpendicular components (x,y),
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -\nabla_{\perp}^2\mathcal{E}-n^2k^2 \mathcal{E},
\end{equation}
This differential equation can be solved by assuming a plane wave expansion $\mathcal{E}(x,y,z)=e^{i(k_x x + k_y y)}f(z)$ which results in
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -(n^2k^2 - k_{\perp}^2)\mathcal{E}.
\end{equation}
The solution to this equation is the so called Angular Spectrum Propagator that relates the electric field at any one plane to the electric field at any other,
\begin{equation}
\label{eq:angular_spectrum}
\mathcal{E}(x, y, z') = \mathcal{F}_{x,y}^{-1}\{e^{-ik_z(z'-z)}\mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}

Here the $z$ component of the wave vector is defined as $k_z=\sqrt{n^2k^2 - k_{\perp}^2}$ and $\mathcal{F}_{x,y}^{(-1)}$ is defined as the (inverse) Fourier transform over the x and y coordinates.
%
While Equation \ref{eq:angular_spectrum} describes the full propagation from one plane to another, it is quite unwieldy to use and does not provide much physical insight.
%
For many optical systems it is sufficient to analyze the paraxial performance.
%
The paraxial approximation assumes that the plane waves make small angles with respect to the z-axis which means that the $x$ and $y$ wave vector components are $k_x,k_y<<1$.
%
In this regime the propagation factor $k_z=\sqrt{n^2k^2 - k_{\perp}^2}\approx nk - \frac{k_{\perp}^2}{2nk}$ and the Fresnel propagation equation becomes
\begin{equation}
\label{eq:angular_spectrum2}
\mathcal{E}(x, y, z') = e^{-ink(z'-z)} \mathcal{F}_{x,y}^{-1}\{ e^{-i\frac{k_{\perp}^2}{2nk}} \mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}
The real space solution that is derived from the propagation equation is the classical Fresnel diffraction equation,
\begin{equation}
\label{eq:fresnel_diffraction}
\mathcal{E}(x, y, z') = \frac{e^{-ink(z'-z)}}{\lambda z} \iint_{-\infty}^{\infty} \mathcal{E}(u, v, z) e^{\frac{ik\left[(x - u)^2 + (y - v)^2\right]}{2 (z' - z)}} \mathrm{d}u \mathrm{d}v.
\end{equation}
The far-field approximation ($z \gg x, y$) and the substitution $\theta_x = \frac{x}{\lambda z}$, $\theta_y = \frac{y}{\lambda z}$ results in the Fraunhofer diffraction integral,
\begin{equation}
\label{eq:fraunhofer_diffraction}
\mathcal{E}(\theta_x, 
\theta_y) \propto \iint_{-\infty}^{\infty} \mathcal{E}(u, v) e^{-i2\pi(\theta_x u + \theta_y v)} \mathrm{d}u \mathrm{d}v.
\end{equation}
This shows that the far-field distribution of an electromagnetic wave is it's Fourier transform. A perfectly aligned lens, or the mirrors of a telescope, brings rays that come from infinity to the focal point. This is identical to a far-field transform, and therefore the operation of a lens can be described by the Fraunhofer diffraction integral.

The \ac{psf} is defined as the response function of an optical system to a point source at infinity.
%
We show the \acp{psf} (defined as the square of the Fourier transform of the telescope pupil $\Pi$) equal to $|\mathcal{F}_{x,y}[\Pi]|^2$ for several telescope pupils seen in Figure~\ref{fig:telpsfs}.

\begin{figure}[ht]
  \centering
  \script{plot_telescope_psfs.py}
  \includegraphics[width=1.0\linewidth]{figures/telescope_psfs.pdf}
  \caption{Telescope pupils and their \acp{psf} for several ground and space based telescopes.
  % 
  \acp{psf} have been normalised to the peak of the \ac{psf} and are on a logarithmic scale down to $10^{-6}$.}
  \label{fig:telpsfs}
\end{figure}

\section{The Lyot Coronagraph}

Stellar coronagraphs have now been in use for several decades.
%
However, the first coronagraph was developed by Bernard Lyot to observe the corona of the Sun in the 1930s \citep{Lyot39}.
%
It took over half a century before astronomers applied coronagraphs to image the faint circumstellar environment by blocking starlight.

\begin{figure}[ht]
  \centering
%  \script{plot_scale_invariant_masks.py}
  \includegraphics[width=0.95\linewidth]{figures/lyot.pdf}
  \caption{The Lyot coronagraph.
  %
  A telescope with a circular unobstructed pupil (image A) points at a star along the optical axis of the telescope and instrument.
  %
  The telescope pupil is reimaged through the instrument optics to a focal plane seen at B, showing an Airy core surrounded by diffraction rings.
  %
  A \acl{fpm} then blocks the central region of the stellar image, resulting in the image seen at C.
  %
  Another set of optics reimages C to a pupil plane at D.
  %
  The removal of the Airy core at the \acl{fpm} redistributes light into a broad ring around the edge of the reimaged telescope pupil.
  %
  The Lyot stop (more generally referred to as a \acl{ppm}) blocks this star light, at a cost of reduced off-axis throughput and decreased angular resolution.
  %
  A final set of relay optics then form the \acl{scfp} at F.}
  \label{fig:lyot}
\end{figure}

The first coronagraph to successfully image a debris disk was a Lyot coronagraph built by \citet{Vilas87} and it imaged the edge-on circumstellar disk around Beta Pictoris in 1984 \citep{Smith84}.
%
The optical layout of the Lyot coronagraph can be generalised in Figure~\ref{fig:lyot}, with the letters A-F representing the images present at that location in the coronagraph light path.
%
The telescope pupil (A) is reimaged into a focal plane of the sky (B) where a \ac{fpm} that has high absorptivity and low reflectivity blocks the light from any on-axis source (C).
%
Optics then form an image of the resultant pupil (D) to an intermediate \ac{pp}, where a \ac{ppm} - the Lyot stop - is located.
%
The diffraction of starlight around the \ac{fpm} results in a ring of light around the diameter of the reimaged telescope pupil (D), and Lyot stop blocks this ring of light.
%
A second optical system then reimages this light onto the \ac{scfp} (F).
%
Any circumstellar objects outside the radius of the \ac{fpm} then pass through unimpeded through the coronagraph and are subsequently reimaged in the \ac{scfp}.
%
The light rays pass through the coronagraph optics to form an image at F with only minor modification: the reimaged pupil at D is superficially very similar to the telescope pupil A.

\begin{armarginnote}[]
\acc{fpm}
\acc{ppm}
\acc{scfp}
\end{armarginnote}

For an on-axis source, the removal of the Airy core plus attendant diffraction rings significantly modifies the wavefront passing through the coronagraph, resulting in a flux redistribution at D where the flux is concentrated in a ring whose peak brightness lies along the perimeter of the reimaged telescope pupil, extending both beyond the radius of the pupil and into the centre of the pupil.
%
The purpose of the Lyot stop is to remove as much of this ring of light as possible, whilst maximising the throughput of the pupil image D for off-axis sources.
%
Decreasing the diameter of the \ac{fpm} changes the \ac{fwhm} of the ring of light at D, which requires a smaller Lyot stop to block - but the throughput of the pupil for off-axis sources then decreases.
%
Decreasing the Lyot stop aperture has a second impact in that the reduced pupil diameter increases the \ac{fwhm} of the images in the final focal plane F, spreading the flux from the off-axis sources over a larger area in the detector and degrading the angular resolution of the telescope and instrument.
%
The optimal diameters of the \ac{fpm} and Lyot stop aperture are then driven by the science requirements - how close to the central star (measured in diffraction widths at the lower spatial resolution) should the coronagraph be able to transmit light from off-axis objects in the field of view.

\section{Parameters to optimize}

Clear apertures (ones with no secondary obscurations that block light from a simple circular aperture) can have solutions that perfectly remove any on-axis light.
%
However, real systems are not ideal and generally don't have a clear aperture.
%
Even more importantly, stars are not ideal point sources.
%
Solutions that only work for point sources are already out of the question then.
%
The current and future generation of coronagraphs are designed to take on non-ideal environments.
%
This means that the coronagraph is optimized for a specific list of parameters during the design process.

\begin{armarginnote}[]
\acc{iwa}
\acc{owa}
\end{armarginnote}
